Dish: Distribution-oblivious Shell Scripting

### 2019-11-23 pldi/draft.tex
Update table

\begin{table*}[t]
\center
\footnotesize
% \setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Summary of Micro-benchmarks}.
    The micro-benchmarks are small pipelines (\ie ones developed on-the-fly) drawn from various sources and applied to large datasets.
  }
}
\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} llllll}
\toprule
  Script                 ~&~ Structure                    & Input (MB)& Time (Seq)    & Script Size (LoC)             & Highlights                                        \\
\midrule
% https://github.com/andromeda/sdsh/blob/master/scripts/grep.sh
  \tti{min-grep}         ~&~$3\times$\tsta                &           &               &   17\qquad 134\qquad  1304    & complex NFA regex                                 \\
% https://github.com/andromeda/sdsh/blob/master/scripts/minimal5.sh
  \tti{min-sort}         ~&~~$\tsta, \tpur$               &           &               &   X \qquad 129\qquad  1209    & \tti{sort}ing                                     \\
% https://github.com/andromeda/sdsh/blob/master/scripts/topn.sh
  \tti{wf}               ~&~~$3\times\tsta, 3\times\tpur$ &           &               &   X \qquad 181\qquad  1621    & double \tti{sort}, \tti{uniq} reduction           \\
% https://github.com/andromeda/sdsh/blob/master/scripts/topn.sh
  \tti{top-n}            ~&~~$2\times\tsta, 4\times\tpur$ &           &               &   X \qquad 181\qquad  1621    & double \tti{sort}, \tti{uniq} reduction           \\
% https://github.com/andromeda/sdsh/blob/master/scripts/ngrams.sh
  \tti{bi-gram}          ~&~~$2\times\tsta, 4\times\tpur$ &           &               &   X \qquad  X \qquad          & stream shifting and merging                       \\
% https://github.com/andromeda/sdsh/blob/master/scripts/spell.sh
  \tti{spell}            ~&~~$4\times\tsta, 3\times\tpur$ &           &               &  37 \qquad 257\qquad  2417    & comparisons (\tti{comm})                          \\
% https://github.com/andromeda/sdsh/blob/master/scripts/diff.sh
  \tti{diff}             ~&~~$4\times\tsta, 3\times\tpur$ &           &               &   X \qquad  X \qquad          & shuffling and non-distributable \tti{diff}ing     \\
\bottomrule
\end{tabular*}
\label{tab:eval}
\end{table*}

@@

Input sizes and times (col. 2, 3) summarize the longest sequential execution (200 files in Fig.~\ref{fig:microbenchmarks}).
Script sizes report on the \sys's rewritten output for three different distribution sizes---$1\times$, 10$\times$, and $100\times$.

>>>>

\begin{table*}[t]
\center
\footnotesize
% \setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Summary of Micro-benchmarks}.
    The micro-benchmarks are small pipelines (\ie ones developed on-the-fly) drawn from various sources and applied to large datasets.
  }
}
\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} llllll}
\toprule
  Script                 ~&~ Structure                    & Input (MB)& Time (Seq)    & Script Size (LoC)             & Highlights                                        \\
\midrule
% https://github.com/andromeda/sdsh/blob/master/scripts/grep.sh
  \tti{min-grep}         ~&~$3\times$\tsta                & 1000      &  78m 36.77s   &   30\qquad 134\qquad  1304    & complex NFA regex                                 \\
% https://github.com/andromeda/sdsh/blob/master/scripts/minimal5.sh
  \tti{min-sort}         ~&~~$\tsta, \tpur$               & 10000     &  23m 19.85s   &   33\qquad 129\qquad  1209    & \tti{sort}ing                                     \\
% https://github.com/andromeda/sdsh/blob/master/scripts/topn.sh
  \tti{wf}               ~&~~$3\times\tsta, 3\times\tpur$ & 1000      &   2m 11.18s   &   53\qquad 181\qquad  1621    & double \tti{sort}, \tti{uniq} reduction           \\
% https://github.com/andromeda/sdsh/blob/master/scripts/topn.sh
  \tti{top-n}            ~&~~$2\times\tsta, 4\times\tpur$ & 1000      &   6m 53.55s   &   53\qquad 181\qquad  1621    & double \tti{sort}, \tti{uniq} reduction           \\
% https://github.com/andromeda/sdsh/blob/master/scripts/ngrams.sh
  \tti{bi-gram}          ~&~~$2\times\tsta, 4\times\tpur$ & \todo{X}  &               &   X \qquad  X \qquad          & stream shifting and merging                       \\
% https://github.com/andromeda/sdsh/blob/master/scripts/spell.sh
  \tti{spell}            ~&~~$4\times\tsta, 3\times\tpur$ & 1000      &   8m 13.42s   &  37 \qquad 257\qquad  2417    & comparisons (\tti{comm})                          \\
% https://github.com/andromeda/sdsh/blob/master/scripts/diff.sh
  \tti{diff}             ~&~~$4\times\tsta, 3\times\tpur$ & \todo{X}  &               &   X \qquad  X \qquad          & shuffling and non-distributable \tti{diff}ing     \\
\bottomrule
\end{tabular*}
\label{tab:eval}
\end{table*}

@@

Input sizes and times (col. 2, 3) summarize the longest sequential execution (200 files in Fig.~\ref{fig:microbenchmarks}).
Script sizes report on the \sys's rewritten output for three different distribution sizes---$2\times$, 10$\times$, and $100\times$.
